Errata

### 2025-04-05 tex/Manuscript-1.tex
Update dissertation files with new manuscript details, remove discussion section, and refine formatting

>>>>

\begin{center}
    \textbf{\Large Manuscript 1}

    \vspace{2cm}
    \textit{SOIL, 8, 717–731, 2022}\\
    \textit{DOI: 10.5194/soil-8-717-2022}

    \vspace{1.5cm}

    Nicolás Riveras-Muñoz\textsuperscript{1*}, Steffen Seitz\textsuperscript{1}, Kristina Witzgall\textsuperscript{2}, Victoria Rodríguez\textsuperscript{3}, Peter Kühn\textsuperscript{1}, Carsten W. Mueller\textsuperscript{4}, Rómulo Oses\textsuperscript{5}, Oscar Seguel\textsuperscript{6}, Dirk Wagner\textsuperscript{3,7}, and Thomas Scholten\textsuperscript{1}

    \vspace{1cm}

    \textsuperscript{1}University of Tübingen, Department of Geosciences, Soil Science and Geomorphology, Rümelinstr. 19-23, 72070 Tübingen, Germany
    \vspace{0.5cm}
    \textsuperscript{2}Technical University of Munich, Soil Science, Emil-Ramann-Str. 2, 85354 Freising, Germany
    \vspace{0.5cm}
    \textsuperscript{3}GFZ German Research Centre for Geosciences, Section 5.3 Geomicrobiology, Telegrafenberg, 14473 Potsdam, Germany
    \vspace{0.5cm}
    \textsuperscript{4}Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark
    \vspace{0.5cm}
    \textsuperscript{5}Universidad de Atacama, Centro Regional de Investigación y Desarrollo Sustentable de Atacama (CRIDESAT), Copayapu 485, Copiapó, Chile
    \vspace{0.5cm}
    \textsuperscript{6}Universidad de Chile, Facultad de Ciencias Agronómicas, Av. Santa Rosa #11315, La Pintana, 8820808 Santiago, Chile
    \vspace{0.5cm}
    \textsuperscript{7}University of Potsdam, Institute of Geosciences, Karl-Liebknecht-Str. 24-25, 14476 Potsdam, Germany
    \vspace{2cm}

    Submitted: March 07, 2022\\
    Accepted: October 22, 2022\\
    Published: December 07, 2022
\end{center}
